---
title: "Toxic metal mixtures in wells and PTB: metal mixtures models"
author: "Lauren Eaves"
date: "04/06/2022"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sessionInfo()
rm(list=ls())

#install.packages("yaml")
#install.packages("rmarkdown")
#install.packages("broom")

#install.packages("devtools")
#library(devtools)
#devtools::install_github("alexpkeil1/qgcompint")

library(tidyverse)
library(ggplot2)
library(knitr)
library(yaml)
library(rmarkdown)
library(broom)
library(ggpubr)
library(qgcomp)
library(qgcompint)

#Create a current date variable to name outputfiles
cur_date <- str_replace_all(Sys.Date(),"-","")

#Create an output folder 
Output_Folder <- ("/Users/lauren_eaves/IEHS Dropbox/lauren Eaves/2_Dissertation/2_Analysis/Aim 2/1_analysis/output")

#Load cohort data - generated in script: 1_20220131_cohortdataprep
cohort <- read.csv(file="output/20220405_NCbirths_NAsingletons_GAexclusions_tractlevelmetals_data_withexposurevars.csv")
colnames(cohort)

```


#Covariate variables generation
```{r}

#ensure covariates are in correct variable type form 
cohort <- cohort %>% 
  mutate(racegp = as.factor(racegp)) %>% 
  mutate(mage = as.numeric(mage)) %>% 
  mutate(mage_sq = as.numeric(mage_sq)) %>% 
  mutate(smoke = as.numeric(smoke)) %>% 
  mutate(season_concep = as.factor(season_concep)) %>% 
  mutate(mothed = as.numeric(mothed)) %>% 
  mutate(Nitr_perc = as.numeric(Nitr_perc)) %>% 
  mutate(sex = as.factor(sex))%>% 
  mutate(pov_perc = as.numeric(pov_perc))

cohort <- cohort %>% 
  mutate(preterm = as.factor(preterm)) %>% 
  mutate(verypreterm = as.factor(verypreterm)) %>% 
  mutate(extremepreterm = as.factor(extremepreterm))
cohort$preterm <- relevel(cohort$preterm, ref = "0")
cohort$verypreterm <- relevel(cohort$verypreterm, ref = "0")
cohort$extremepreterm <- relevel(cohort$extremepreterm, ref = "0")

```

# PTB mixture models
```{r}
colnames(cohort)

Xnm <- c('Arsenic.Mean_avg', 'Cadmium.Mean_avg', 'Lead.Mean_avg', 'Manganese.Mean_avg', 'Chromium.Mean_avg', 'Copper.Mean_avg', 'Zinc.Mean_avg')
covars = c('mage','mage_sq','racegp','smoke','season_concep','mothed','Nitr_perc','pov_perc')


PTB_adj_ppb <- qgcomp.noboot(preterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,covars,'preterm')], family=binomial(), q=4)
PTB_adj_ppb
plot(PTB_adj_ppb)


PTB_unadj_ppb <- qgcomp.noboot(preterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,'preterm')], family=binomial(), q=4)
PTB_unadj_ppb
plot(PTB_unadj_ppb)



```
# PTB mixture models: partial effects, adjusted  
```{r}
# training/validation split
set.seed(432789)
trainidx <- sample(1:nrow(cohort), round(nrow(cohort)*0.3))
valididx <- setdiff(1:nrow(cohort),trainidx)
traindata <- cohort[trainidx,]
validdata <- cohort[valididx,]
dim(traindata) 
dim(validdata)  

PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#assessing effect one covariate at a time 
#no poverty 
covars = c('mage','mage_sq','racegp','smoke','season_concep','mothed','Nitr_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no nirtrites
covars = c('mage','mage_sq','racegp','smoke','season_concep','mothed','pov_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no maternal education 
covars = c('mage','mage_sq','racegp','smoke','season_concep','Nitr_perc','pov_perc')

PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no season concept
covars = c('mage','mage_sq','racegp','smoke','mothed','Nitr_perc','pov_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no smoking
covars = c('mage','mage_sq','racegp','season_concep','mothed','Nitr_perc','pov_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no race/eth
covars = c('mage','mage_sq','smoke','season_concep','mothed','Nitr_perc','pov_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights

#no maternal age 
covars = c('racegp','smoke','season_concep','mothed','Nitr_perc','pov_perc')
PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres
plot(PTB_splitres$pos.fit)
plot(PTB_splitres$neg.fit)

PTB_splitres$posmix
PTB_splitres$pos.fit$pos.weights
PTB_splitres$pos.fit$neg.weights
PTB_splitres$negmix
PTB_splitres$neg.fit$pos.weights
PTB_splitres$neg.fit$neg.weights













```

# PTB mixture models: partial effects, unadjusted  
```{r}
# training/validation split
set.seed(432789)
trainidx <- sample(1:nrow(cohort), round(nrow(cohort)*0.3))
valididx <- setdiff(1:nrow(cohort),trainidx)
traindata <- cohort[trainidx,]
validdata <- cohort[valididx,]
dim(traindata) 
dim(validdata)  

PTB_splitres_unadj <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,'preterm')],
                                validdata=validdata[,c(Xnm,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
PTB_splitres_unadj
plot(PTB_splitres_unadj$pos.fit)
plot(PTB_splitres_unadj$neg.fit)

PTB_splitres_unadj$posmix
PTB_splitres_unadj$pos.fit$pos.weights
PTB_splitres_unadj$pos.fit$neg.weights
PTB_splitres_unadj$negmix
PTB_splitres_unadj$neg.fit$pos.weights
PTB_splitres_unadj$neg.fit$neg.weights

```

# very PTB mixture models
```{r}

vPTB_adj_ppb <- qgcomp.noboot(verypreterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,covars,'verypreterm')], family=binomial(), q=4)
vPTB_adj_ppb
plot(vPTB_adj_ppb)

vPTB_unadj_ppb <- qgcomp.noboot(verypreterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,'verypreterm')], family=binomial(), q=4)
vPTB_unadj_ppb
plot(vPTB_unadj_ppb)


```

# very PTB mixture models: partial effects, adjusted 
```{r}

vPTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=verypreterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'verypreterm')],
                                validdata=validdata[,c(Xnm,covars,'verypreterm')], 
                                expnms=Xnm,
                                family=binomial())
vPTB_splitres
plot(vPTB_splitres$pos.fit)
plot(vPTB_splitres$neg.fit)


vPTB_splitres$posmix
vPTB_splitres$pos.fit$pos.weights
vPTB_splitres$pos.fit$neg.weights
vPTB_splitres$negmix
vPTB_splitres$neg.fit$pos.weights
vPTB_splitres$neg.fit$neg.weights

```

# very PTB mixture models: partial effects, unadjusted 
```{r}

vPTB_splitres_unadj <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=verypreterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,'verypreterm')],
                                validdata=validdata[,c(Xnm,'verypreterm')], 
                                expnms=Xnm,
                                family=binomial())
vPTB_splitres_unadj
plot(vPTB_splitres_unadj$pos.fit)
plot(vPTB_splitres_unadj$neg.fit)


vPTB_splitres_unadj$posmix
vPTB_splitres_unadj$pos.fit$pos.weights
vPTB_splitres_unadj$pos.fit$neg.weights
vPTB_splitres_unadj$negmix
vPTB_splitres_unadj$neg.fit$pos.weights
vPTB_splitres_unadj$neg.fit$neg.weights

```

# extreme PTB mixture models
```{r}

ePTB_adj_ppb <- qgcomp.noboot(extremepreterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,covars,'extremepreterm')], family=binomial(), q=4)
ePTB_adj_ppb
plot(ePTB_adj_ppb)

ePTB_unadj_ppb <- qgcomp.noboot(extremepreterm~.,
                          expnms=Xnm, dat=cohort[,c(Xnm,'extremepreterm')], family=binomial(), q=4)
ePTB_unadj_ppb
plot(ePTB_unadj_ppb)

```

# extremely PTB mixture models: partial effects, adjusted  
```{r}

ePTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=extremepreterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'extremepreterm')],
                                validdata=validdata[,c(Xnm,covars,'extremepreterm')], 
                                expnms=Xnm,
                                family=binomial())
ePTB_splitres
plot(ePTB_splitres$pos.fit)
plot(ePTB_splitres$neg.fit)

ePTB_splitres$posmix
ePTB_splitres$pos.fit$pos.weights
ePTB_splitres$pos.fit$neg.weights
ePTB_splitres$negmix
ePTB_splitres$neg.fit$pos.weights
ePTB_splitres$neg.fit$neg.weights

```
# extremely PTB mixture models: partial effects, unadjusted
```{r}

ePTB_splitres_unadj <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=extremepreterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,'extremepreterm')],
                                validdata=validdata[,c(Xnm,'extremepreterm')], 
                                expnms=Xnm,
                                family=binomial())
ePTB_splitres_unadj
plot(ePTB_splitres_unadj$pos.fit)
plot(ePTB_splitres_unadj$neg.fit)

ePTB_splitres_unadj$posmix
ePTB_splitres_unadj$pos.fit$pos.weights
ePTB_splitres_unadj$pos.fit$neg.weights
ePTB_splitres_unadj$negmix
ePTB_splitres_unadj$neg.fit$pos.weights
ePTB_splitres_unadj$neg.fit$neg.weights

```


# Export results 
```{r}
allmodels <- c("PTB_unadj_ppb", "PTB_adj_ppb", 
               "vPTB_unadj_ppb", "vPTB_adj_ppb", 
               "ePTB_unadj_ppb", "ePTB_adj_ppb", 
               "PTB_splitres$pos.fit","vPTB_splitres$pos.fit","ePTB_splitres$pos.fit",
               "PTB_splitres$neg.fit","vPTB_splitres$neg.fit","ePTB_splitres$neg.fit",
               "PTB_splitres_unadj$pos.fit","vPTB_splitres_unadj$pos.fit","ePTB_splitres_unadj$pos.fit",
               "PTB_splitres_unadj$neg.fit","vPTB_splitres_unadj$neg.fit","ePTB_splitres_unadj$neg.fit")


# SLOPE PARAMETERS
clean_print <- function(x){
  output  = data.frame(
    x$coef,
    sqrt(x$var.coef),
    x$ci.coef,
    x$pval
  )
  names(output) = c("Estimate", "Std. Error", "Lower CI", "Upper CI", "p value")
  return(output)
}

Results_SlopeParams <- data.frame() #empty vector to append dfs to
for (i in allmodels){
  print(i)
  df <- eval(parse(text = paste0("clean_print(",i,")"))) %>%
    rownames_to_column("Parameter") %>%
    mutate("Model" = i) 
  Results_SlopeParams <- rbind(Results_SlopeParams,df)
}
Results_SlopeParams <- Results_SlopeParams %>% 
  mutate(OR=exp(Estimate)) %>% 
  mutate(UpperCI_OR=exp(`Upper CI`)) %>% 
  mutate(LowerCI_OR=exp(`Lower CI`))

# METAL COEFFICIENTS
Results_MetalCoeffs <- data.frame()
for (i in allmodels){
  print(i)
  df <- eval(parse(text = paste0("as.data.frame(summary(",i,"$fit)$coefficients[,])"))) %>% 
    mutate("Model" = i)
  df <- df %>% rownames_to_column(var="variable")  
  Results_MetalCoeffs<- rbind(Results_MetalCoeffs,df)
}


# WEIGHTS
# Organizing the weights into one dataframe:
Results_MetalWeights <- data.frame()
for (i in allmodels){
  Results_PWeights <- eval(parse(text = paste0("as.data.frame(",i,"$pos.weights)"))) %>%
    rownames_to_column("Metal") %>%
    dplyr::rename("Weight" = 2) %>%
    mutate("Weight Direction" = "Positive")
  Results_NWeights <- eval(parse(text = paste0("as.data.frame(",i,"$neg.weights)"))) %>%
    rownames_to_column("Metal") %>%
    dplyr::rename("Weight" = 2) %>%
    mutate("Weight Direction" = "Negative")
  Results_Weights <- rbind(Results_PWeights, Results_NWeights) %>%
    mutate("Model" = i) %>% as.data.frame()
  #Merge
  Results_MetalWeights <- rbind(Results_MetalWeights, Results_Weights)
}

write.csv(Results_SlopeParams, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_SlopeParams.csv"), row.names=TRUE)
write.csv(Results_MetalCoeffs, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_MetalCoeffs.csv"), row.names=TRUE)
write.csv(Results_MetalWeights, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_MetalWeights.csv"), row.names=TRUE)

rm(list=c(allmodels))

```

#Race effect measure modification

## Preterm birth 
```{r}

covars = c('mage','mage_sq','smoke','mothed','Nitr_perc','pov_perc')
cohort$racegp <- relevel(cohort$racegp, ref = "1")

PTB_emm <- qgcomp.emm.noboot(preterm~ Arsenic.Mean_avg + Cadmium.Mean_avg + Lead.Mean_avg + Manganese.Mean_avg + Chromium.Mean_avg + Copper.Mean_avg +Zinc.Mean_avg + mage+ mage_sq + smoke + mothed + Nitr_perc,
           emmvar="racegp", 
           expnms = Xnm, 
           dat=cohort[,c(Xnm,covars,'racegp','preterm')], q=4, 
           family=binomial())

PTB_emm

# stratum specific mixture log-odds ratios
getstrateffects(PTB_emm, emmval = "1") #white nonH
getstrateffects(PTB_emm, emmval = "2") #black nonH
getstrateffects(PTB_emm, emmval = "3") #hisp
getstrateffects(PTB_emm, emmval = "4") #asian/PI
getstrateffects(PTB_emm, emmval = "5") #American Ind
getstrateffects(PTB_emm, emmval = "6") #other 

# jointly exposed mixture log-odds ratios
getjointeffects(PTB_emm, emmval = "1") #white nonH
getjointeffects(PTB_emm, emmval = "2") #black nonH
getjointeffects(PTB_emm, emmval = "3") #hisp
getjointeffects(PTB_emm, emmval = "4") #asian/PI
getjointeffects(PTB_emm, emmval = "5") #American Ind
getjointeffects(PTB_emm, emmval = "6") #other 


```


## Very Preterm birth 
```{r}

vPTB_emm <- qgcomp.emm.noboot(verypreterm~ Arsenic.Mean_avg + Cadmium.Mean_avg + Lead.Mean_avg + Manganese.Mean_avg + Chromium.Mean_avg + Copper.Mean_avg +Zinc.Mean_avg + mage+ mage_sq + smoke + mothed + Nitr_perc,
           emmvar="racegp", 
           expnms = Xnm, 
           dat=cohort[,c(Xnm,covars,'racegp','verypreterm')], q=4, 
           family=binomial())

vPTB_emm

# stratum specific mixture log-odds ratios
getstrateffects(vPTB_emm, emmval = "1") #white nonH
getstrateffects(vPTB_emm, emmval = "2") #black nonH
getstrateffects(vPTB_emm, emmval = "3") #hisp
getstrateffects(vPTB_emm, emmval = "4") #asian/PI
getstrateffects(vPTB_emm, emmval = "5") #American Ind
getstrateffects(vPTB_emm, emmval = "6") #other 

# jointly exposed mixture log-odds ratios
getjointeffects(vPTB_emm, emmval = "1") #white nonH
getjointeffects(vPTB_emm, emmval = "2") #black nonH
getjointeffects(vPTB_emm, emmval = "3") #hisp
getjointeffects(vPTB_emm, emmval = "4") #asian/PI
getjointeffects(vPTB_emm, emmval = "5") #American Ind
getjointeffects(vPTB_emm, emmval = "6") #other 


```

## Extremely Preterm birth 
```{r}


ePTB_emm <- qgcomp.emm.noboot(extremepreterm~ Arsenic.Mean_avg + Cadmium.Mean_avg + Lead.Mean_avg + Manganese.Mean_avg + Chromium.Mean_avg + Copper.Mean_avg +Zinc.Mean_avg + mage+ mage_sq + smoke + mothed + Nitr_perc,
           emmvar="racegp", 
           expnms = Xnm, 
           dat=cohort[,c(Xnm,covars,'racegp','extremepreterm')], q=4, 
           family=binomial())

ePTB_emm

# stratum specific mixture log-odds ratios
getstrateffects(ePTB_emm, emmval = "1") #white nonH
getstrateffects(ePTB_emm, emmval = "2") #black nonH
getstrateffects(ePTB_emm, emmval = "3") #hisp
getstrateffects(ePTB_emm, emmval = "4") #asian/PI
getstrateffects(ePTB_emm, emmval = "5") #American Ind
getstrateffects(ePTB_emm, emmval = "6") #other 

# jointly exposed mixture log-odds ratios
getjointeffects(ePTB_emm, emmval = "1") #white nonH
getjointeffects(ePTB_emm, emmval = "2") #black nonH
getjointeffects(ePTB_emm, emmval = "3") #hisp
getjointeffects(ePTB_emm, emmval = "4") #asian/PI
getjointeffects(ePTB_emm, emmval = "5") #American Ind
getjointeffects(ePTB_emm, emmval = "6") #other 


```


# Export race stratification results 
```{r}

all <- mget(ls(pattern="emm"))
allnames <-names(all)
print(allnames)

# SLOPE PARAMETERS
Results_SlopeParams <- data.frame() #empty vector to append dfs to
for (i in allnames){
  print(i)
  df <- eval(parse(text = paste0("clean_print(",i,")"))) %>%
    rownames_to_column("Parameter") %>%
    mutate("Model" = i) 
  Results_SlopeParams <- rbind(Results_SlopeParams,df)
}
Results_SlopeParams <- Results_SlopeParams %>% 
  mutate(OR=exp(Estimate)) %>% 
  mutate(UpperCI_OR=exp(`Upper CI`)) %>% 
  mutate(LowerCI_OR=exp(`Lower CI`))

# METAL COEFFICIENTS
Results_MetalCoeffs <- data.frame()
for (i in allnames){
  print(i)
  df <- eval(parse(text = paste0("as.data.frame(summary(",i,"$fit)$coefficients[,])"))) %>% 
    mutate("Model" = i)
  df <- df %>% rownames_to_column(var="variable")  
  Results_MetalCoeffs<- rbind(Results_MetalCoeffs,df)
}


# WEIGHTS
# Organizing the weights into one dataframe:
Results_MetalWeights <- data.frame()
for (i in allnames){
  Results_PWeights <- eval(parse(text = paste0("as.data.frame(",i,"$pos.weights)"))) %>%
    rownames_to_column("Metal") %>%
    dplyr::rename("Weight" = 2) %>%
    mutate("Weight Direction" = "Positive")
  Results_NWeights <- eval(parse(text = paste0("as.data.frame(",i,"$neg.weights)"))) %>%
    rownames_to_column("Metal") %>%
    dplyr::rename("Weight" = 2) %>%
    mutate("Weight Direction" = "Negative")
  Results_Weights <- rbind(Results_PWeights, Results_NWeights) %>%
    mutate("Model" = i) %>% as.data.frame()
  #Merge
  Results_MetalWeights <- rbind(Results_MetalWeights, Results_Weights)
}

write.csv(Results_SlopeParams, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_SlopeParams_Racemodification.csv"), row.names=TRUE)
write.csv(Results_MetalCoeffs, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_MetalCoeffs_Racemodification.csv"), row.names=TRUE)
write.csv(Results_MetalWeights, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_MetalWeights_Racemodification.csv"), row.names=TRUE)

rm(list=allnames)

```


#PTB mixture models: partial effects, repeats 
```{r}
for (i in 1:5) {
  round <- i
  round <- as.name(round)
  print(round)
  
  n <- runif(1,1,3000000)
  set.seed(n)
  print(n)
  
  trainidx <- sample(1:nrow(cohort), round(nrow(cohort)*0.3))
  valididx <- setdiff(1:nrow(cohort),trainidx)
  traindata <- cohort[trainidx,]
  validdata <- cohort[valididx,]
  
  PTB_splitres <- qgcomp.partials(fun="qgcomp.noboot", 
                                f=preterm~., 
                                q=4, 
                                traindata=traindata[,c(Xnm,covars,'preterm')],
                                validdata=validdata[,c(Xnm,covars,'preterm')], 
                                expnms=Xnm,
                                family=binomial())
  PTB_splitres
  plot(PTB_splitres$pos.fit)
  plot(PTB_splitres$neg.fit)

  PTB_splitres$posmix
  posfit_posweight <- as.data.frame(PTB_splitres$pos.fit$pos.weights) %>% 
    mutate("round"=paste0(round))
  posfit_negweight <- as.data.frame(PTB_splitres$pos.fit$neg.weights)%>% 
    mutate("round"=paste0(round))
  PTB_splitres$negmix
  negfit_posweight <- as.data.frame(PTB_splitres$neg.fit$pos.weights)%>% 
    mutate("round"=paste0(round))
  negfit_negweight <- as.data.frame(PTB_splitres$neg.fit$neg.weights)%>% 
    mutate("round"=paste0(round))
  
  assign(paste0("round",round,"_PTB_splitres"),PTB_splitres) 
  assign(paste0("round",round,"_posfit"),PTB_splitres$pos.fit)
  assign(paste0("round",round,"_negfit"),PTB_splitres$neg.fit)
  assign(paste0("round",round,"_posfit_posweight"),posfit_posweight) 
  assign(paste0("round",round,"_posfit_negweight"),posfit_negweight) 
  assign(paste0("round",round,"_negfit_posweight"),negfit_posweight) 
  assign(paste0("round",round,"_negfit_negweight"),negfit_negweight) 
}

#export weights from each round 
negfit_posweight<-grep("[1-7]_negfit_posweight",names(.GlobalEnv),value=TRUE)
negfit_posweight_list_results<-do.call("list",mget(negfit_posweight))
print(names(negfit_posweight_list_results))

negfit_negweight<-grep("[1-7]_negfit_negweight",names(.GlobalEnv),value=TRUE)
negfit_negweight_list_results<-do.call("list",mget(negfit_negweight))
print(names(negfit_negweight_list_results))

posfit_posweight<-grep("[1-7]_posfit_posweight",names(.GlobalEnv),value=TRUE)
posfit_posweight_list_results<-do.call("list",mget(posfit_posweight))
print(names(posfit_posweight_list_results))

posfit_negweight<-grep("[1-7]_posfit_negweight",names(.GlobalEnv),value=TRUE)
posfit_negweight_list_results<-do.call("list",mget(posfit_negweight))
print(names(posfit_negweight_list_results))

combined_negfit_posweight<- bind_rows(negfit_posweight_list_results, .id=NULL)
combined_negfit_negweight <- bind_rows(negfit_negweight_list_results, .id=NULL)
combined_posfit_posweight <- bind_rows(posfit_posweight_list_results, .id=NULL)
combined_posfit_negweight <- bind_rows(posfit_negweight_list_results, .id=NULL)


write.csv(combined_negfit_posweight, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_weights_partialeffectsrepeats_negfitposweight.csv"), row.names=TRUE)
write.csv(combined_negfit_negweight, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_weights_partialeffectsrepeats_negfitnegweight.csv"), row.names=TRUE)
write.csv(combined_posfit_posweight, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_weights_partialeffectsrepeats_posfitposweight.csv"), row.names=TRUE)
write.csv(combined_posfit_negweight, paste0(Output_Folder,"/", cur_date, "_qgcomp_Results_weights_partialeffectsrepeats_posfitnegweight.csv"), row.names=TRUE)


pattern<-grep("fit$",names(.GlobalEnv),value=TRUE)
fit_list_results<-do.call("list",mget(pattern))
print(names(fit_list_results))

pattern2<-grep("splitres$",names(.GlobalEnv),value=TRUE)
splitres_list_results<-do.call("list",mget(pattern2))
print(names(splitres_list_results))

rm(list=c(names(fit_list_results),names(splitres_list_results),names(negfit_posweight_list_results),names(negfit_negweight_list_results),names(posfit_posweight_list_results),names(posfit_negweight_list_results)))


```






