---
title: 'Toxic metal mixtures in wells and PTB: single metal models, well water sensitivity'
author: "Lauren Eaves"
date: "04/05/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sessionInfo()
rm(list=ls())

#install.packages("yaml")
#install.packages("rmarkdown")
#install.packages("broom")
library(tidyverse)
library(ggplot2)
library(knitr)
library(yaml)
library(rmarkdown)
library(broom)
library(ggpubr)

#Create a current date variable to name outputfiles
cur_date <- str_replace_all(Sys.Date(),"-","")

#Create an output folder 
Output_Folder <- ("/Users/lauren_eaves/IEHS Dropbox/lauren Eaves/2_Dissertation/2_Analysis/Aim 2/1_analysis/output/wellwater_sens")

#Load cohort data - generated in script: 20220131_cohortdataprep.Rmd
cohort <- read.csv(file="output/20220405_NCbirths_NAsingletons_GAexclusions_tractlevelmetals_data_withexposurevars.csv")
colnames(cohort)
#created in functional form script 

#Load tracts distributions data 
tracts <- read.csv(file="input/20220209_NCwellwise_tractlevel_ALLTRACTS_distributions.csv")

#load well water use data 
wells <- read.csv(file="input/NC_Tracts_2010_Well_Pop_Sum.csv")

```


#Data prep: variables 
```{r}

#convert outcome variables to factors and ensure correct reference level 
cohort <- cohort %>% 
  mutate(preterm = as.factor(preterm)) %>% 
  mutate(verypreterm = as.factor(verypreterm)) %>% 
  mutate(extremepreterm = as.factor(extremepreterm))
cohort$preterm <- relevel(cohort$preterm, ref = "0")
cohort$verypreterm <- relevel(cohort$verypreterm, ref = "0")
cohort$extremepreterm <- relevel(cohort$extremepreterm, ref = "0")

metals <- c("Arsenic","Cadmium","Chromium", "Copper","Lead","Manganese","Zinc")

cohort <- cohort %>% 
  mutate(Arsenic_perc=as.factor(Arsenic_perc)) %>% 
  mutate(Cadmium_perc=as.factor(Cadmium_perc)) %>% 
  mutate(Chromium_perc=as.factor(Chromium_perc)) %>% 
  mutate(Copper_perc=as.factor(Copper_perc)) %>% 
  mutate(Lead_perc=as.factor(Lead_perc)) %>% 
  mutate(Manganese_perc=as.factor(Manganese_perc)) %>% 
  mutate(Zinc_perc=as.factor(Zinc_perc)) %>% 
  mutate(Arsenic_limit=as.factor(Arsenic_limit)) %>% 
  mutate(Cadmium_limit=as.factor(Cadmium_limit)) %>% 
  mutate(Chromium_limit=as.factor(Chromium_limit)) %>% 
  mutate(Copper_limit=as.factor(Copper_limit)) %>% 
  mutate(Lead_limit=as.factor(Lead_limit)) %>% 
  mutate(Manganese_limit=as.factor(Manganese_limit)) %>% 
  mutate(Zinc_limit=as.factor(Zinc_limit)) 

```


#Data prep: filter to tracts with >50% & 25% on well water 
```{r}
wells <- wells %>% 
  mutate(percent_ww = (sum/POP2010)*100) %>% 
  dplyr::rename(census_tract=FIPS)

cohort <- left_join(cohort, wells, by="census_tract")
#n=1,493,195

cohort_50 <- cohort %>% 
  filter(percent_ww >= 50)
#n=202,897

cohort_25 <- cohort %>% 
  filter(percent_ww >= 25)
#n=445,002

```

#With dataset of tracts with >50% on well water 
#Fit unadjusted models: for preterm birth 
##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(preterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}

```



## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc, 
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_unadjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_unadjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()


```


#Fit unadjusted models: for very preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(verypreterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc,
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_unadjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)

tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_unadjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit unadjusted models: for extremely preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(extremepreterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc,
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_unadjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)

tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_unadjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit adjusted models: for preterm birth  
```{r}

#create covariate variables that need to be derived 
#mage square term 
cohort <- cohort %>% 
  mutate(mage_sq = mage*mage) 

#ensure covariates are in correct variable type form 
cohort <- cohort %>% 
  mutate(racegp = as.factor(racegp)) %>% 
  mutate(mage = as.numeric(mage)) %>% 
  mutate(mage_sq = as.numeric(mage_sq)) %>% 
  mutate(smoke = as.numeric(smoke)) %>% 
  mutate(season_concep = as.factor(season_concep)) %>% 
  mutate(mothed = as.numeric(mothed)) %>% 
  mutate(Nitr_perc = as.numeric(Nitr_perc)) %>% 
  mutate(sex = as.factor(sex))%>% 
  mutate(pov_perc = as.factor(pov_perc))

```

##With percentile variables 
```{r}


for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(preterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}

```


## Merge results 
```{r}
#merge all single metal, adjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_adjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)



tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_adjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()


```

#Fit adjusted models: for very preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(verypreterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, adjusted, very preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_adjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_adjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit adjusted models: for extremely preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_50$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(extremepreterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_50)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, adjusted, very preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_adjusted_models_50wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)

tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_adjusted_models_percplots_50wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```



#With dataset of tracts with >25% on well water 
#Fit unadjusted models: for preterm birth 
##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(preterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}

```

## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc, 
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_unadjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)

tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_unadjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit unadjusted models: for very preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(verypreterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc, 
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_unadjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_unadjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit unadjusted models: for extremely preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(extremepreterm ~ eval(parse(text = paste0(metal,"_perc"))), family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_unadj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_unadj_perc"),mod_tid) 
  assign(paste0(metal,"_unadj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, unadjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_unadj_perc, 
                    Cadmium_unadj_perc, 
                    Chromium_unadj_perc, 
                    Copper_unadj_perc, 
                    Lead_unadj_perc, 
                    Manganese_unadj_perc, 
                    Zinc_unadj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_unadjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_unadj_perc_plot,
                        Cadmium_unadj_perc_plot,
                        Chromium_unadj_perc_plot,
                        Copper_unadj_perc_plot,
                        Lead_unadj_perc_plot,
                        Manganese_unadj_perc_plot,
                        Zinc_unadj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_unadjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()

```


#Fit adjusted models: for preterm birth  
```{r}

#create covariate variables that need to be derived 
#mage square term 
cohort <- cohort %>% 
  mutate(mage_sq = mage*mage) 

#ensure covariates are in correct variable type form 
cohort <- cohort %>% 
  mutate(racegp = as.factor(racegp)) %>% 
  mutate(mage = as.numeric(mage)) %>% 
  mutate(mage_sq = as.numeric(mage_sq)) %>% 
  mutate(smoke = as.numeric(smoke)) %>% 
  mutate(season_concep = as.factor(season_concep)) %>% 
  mutate(mothed = as.numeric(mothed)) %>% 
  mutate(Nitr_perc = as.numeric(Nitr_perc)) %>% 
  mutate(sex = as.factor(sex))%>% 
  mutate(pov_perc = as.factor(pov_perc))

```

##With percentile variables 
```{r}


for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(preterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}

```


## Merge results 
```{r}
#merge all single metal, adjusted, preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_adjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_pretermbirth_singlemetal_adjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()


```

#Fit adjusted models: for very preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(verypreterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}
```


## Merge results 
```{r}
#merge all single metal, adjusted, very preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_adjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_verypretermbirth_singlemetal_adjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()


```


#Fit adjusted models: for extremely preterm birth  

##With percentile variables 
```{r}

for (i in 1:length(metals)) {
  metal <- metals[[i]]
  metal <- as.name(metal)
  print(metal)
  
  print(is.factor(eval(parse(text = paste0("cohort_25$",metal,"_perc"))))) #check that metal var is a factor

  mod <- glm(extremepreterm ~ eval(parse(text = paste0(metal,"_perc"))) + mage + mage_sq+ racegp + smoke + season_concep + mothed + Nitr_perc + pov_perc, family=binomial, data=cohort_25)
  
  mod_tid <- tidy(mod, conf.int=TRUE, conf.level=0.95) %>% 
  mutate(model_name=paste0(metal,"_adj_perc")) %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(OR.conf.high = exp(conf.high)) %>% 
  mutate(OR.conf.low = exp(conf.low)) 

  mod_tid[2,1] <- paste0(metal,"_perc_50to90")
  mod_tid[3,1] <- paste0(metal,"_perc_over90")
  
  plot <- mod_tid %>% 
  filter(grepl('perc', term))%>% 
  ggplot(aes(OR, term, xmin = OR.conf.low, xmax = OR.conf.high, height = 0)) +
  geom_point() +
  scale_x_continuous(trans="log10")+
  geom_errorbarh()
  
  assign(paste0(metal,"_adj_perc"),mod_tid) 
  assign(paste0(metal,"_adj_perc_plot"),plot) 
  
}
```

## Merge results 
```{r}
#merge all single metal, adjusted, very preterm birth models dataframes 
results_df <- rbind(Arsenic_adj_perc, 
                    Cadmium_adj_perc, 
                    Chromium_adj_perc, 
                    Copper_adj_perc, 
                    Lead_adj_perc, 
                    Manganese_adj_perc, 
                    Zinc_adj_perc)
write.csv(results_df, paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_adjusted_models_25wellwater.csv"), row.names= TRUE)

#merge all the plots 
perc_plots <- ggarrange(Arsenic_adj_perc_plot,
                        Cadmium_adj_perc_plot,
                        Chromium_adj_perc_plot,
                        Copper_adj_perc_plot,
                        Lead_adj_perc_plot,
                        Manganese_adj_perc_plot,
                        Zinc_adj_perc_plot)


tiff(file = (paste0(Output_Folder,"/", cur_date, "_NCbirths_extremepretermbirth_singlemetal_adjusted_models_percplots_25wellwater.tiff")), width = 10, height = 8, units = "in", pointsize = 12, res = 300)
plot(perc_plots)
dev.off()


```
